\LaTeXe\ guide for the Journal of Functional Programming

### 2019-05-02 papers/jfp/8-engineering.tex

To legitimise shallow builds, we need to relax the correctness
Definition~\ref{def-correct} as follows. Let the \hs{shallow} store correspond
to the result of a shallow build. Then \hs{shallow} is correct, if \emph{there
exists} a \hs{result} which satisfies all requirements of the
Definition~\ref{def-correct}, \emph{such that} \hs{shallow} agrees with the
\hs{result} on all the input keys \hs{k}~$\in$~$I$:
\[
\hs{getValue}~\hs{k}~\hs{shallow}~\hs{==}~\hs{getValue}~\hs{k}~\hs{result} % \text{,}
\]
and on the target \hs{key}:
\[
\hs{getValue}~\hs{key}~\hs{shallow}~\hs{==}~\hs{getValue}~\hs{key}~\hs{result} % \text{.}
\]

\noindent
This relaxes the requirements on shallow builds by dropping the constraints on
the \hs{shallow} store for all intermediate keys \hs{k}~$\in$~$O\setminus \{\hs{key}\}$.

@@

Deep constructive traces (\S\ref{sec-deep-constructive-traces}) combined with
task non-determinism (\S\ref{sec-non-determinism}) can lead to very subtle bugs,
especially in the cloud setting. Fig.~\ref{fig-frankenbuild} shows a
\emph{Frankenbuild}~\cite{esfahani2016cloudbuild} example, where the target
\cmd{report.txt}, which is downloaded from the cloud, is inconsistent with its
immediate dependency \cmd{main.prof}. This inconsistency is caused by two factors:
(i)~inherent non-determinism of profiling: running a profiling tool on the very
same \cmd{main.exe} will produce different \cmd{main.prof} results every time;
and (ii)~relying on deep constructive traces, which cache build results based
only on the hashes of terminal task inputs (in this case \cmd{main.exe}). Note
that the resulting store is incorrect according to all three definitions of
correctness: the main definition~(\S\ref{sec-build-correctness}), the variant
for non-deterministic tasks~(\S\ref{sec-non-determinism}) and the variant for
shallow builds~(this section).

>>>>

Shallow builds have a slightly weaker correctness property than
Definition~\ref{def-correct}. Instead of demanding that \emph{all} keys reachable
from the target match, we only require matches for the target itself and the \emph{input
keys} reachable from the target.

@@

As described in \S\ref{sec-using-cloud-shake}, non-determinism  (\S\ref{sec-non-determinism})
is harmful for cloud builds, reducing the number of cache hits.
However, for deep constructive traces (\S\ref{sec-deep-constructive-traces}) it
is much worse, even leading to \emph{incorrect results}.
Fig.~\ref{fig-frankenbuild} shows a
\emph{Frankenbuild}~\cite{esfahani2016cloudbuild} example, where the target
\cmd{report.txt}, which is downloaded from the cloud, is inconsistent with its
immediate dependency \cmd{main.prof}. This inconsistency is caused by two factors:
(i)~inherent non-determinism of profiling: running a profiling tool on the very
same \cmd{main.exe} will produce different \cmd{main.prof} results every time;
and (ii)~relying on deep constructive traces, which cache build results based
only on the hashes of terminal task inputs (in this case \cmd{main.exe}). Note
that the resulting store is incorrect according to all three definitions of
correctness: the main definition~(\S\ref{sec-build-correctness}), the variant
for non-deterministic tasks~(\S\ref{sec-non-determinism}) and the variant for
shallow builds~(this section).
